The impacts of public health policy measures on reducing SARS-CoV-2 transmission in Australia

### 2020-05-17 manuscript/ms.Rmd
fix up ms and add modele fitting section

---
title: "The impacts of public health policy measures on reducing SARS-CoV-2 transmission in Australia"
author:
  - Nick Golding$^1$, ...$^2$ & ...$^3$
  - $^1$ Telethon Kids Institute and Curtin University, Perth WA, Australia
  - $^2$ ...
  - $^3$ ...
bibliography: distancing.bib
output:
  pdf_document:
  word_document:
    fig_caption: true
    highlight: null
header-includes: \usepackage{float}
---

@@

  "$q_2 / q_1 \\sim \\mathrm{U}(0, 1)$",
  "Relative effect of quarantine (phase 2 vs 1)",

  "$q_3 / q_2 \\sim \\mathrm{U}(0, 1)$",
  "Relative effect of quarantine (phase 3 vs 2)"

@@

>>>>

---
title: "The impacts of public health policy measures on reducing SARS-CoV-2 transmission in Australia"
author:
  - Nick Golding$^1$, ...$^2$ & ...$^3$
  - $^1$ Telethon Kids Institute and Curtin University, Perth WA, Australia
  - $^2$ ...
  - $^3$ ...
bibliography: distancing.bib
output:
  pdf_document:
    keep_tex: true
  word_document:
    fig_caption: true
    highlight: null
header-includes: \usepackage{float}
---

@@

  "$q_2 \\times q_1 \\sim \\mathrm{U}(0, 1)$",
  "Relative effect of quarantine (phase 2 vs 1)",

  "$q_3 \\times q_2 \\sim \\mathrm{U}(0, 1)$",
  "Relative effect of quarantine (phase 3 vs 2)"

@@

### Model fitting
Inference was performed by Hamiltonian Monte Carlo using the R packages greta and greta.gp [@greta, @greta.gp].
Posterior samples of model parameters were generated by 10 independent chains of a Hamiltonian Monte Carlo sampler, each run for 1000 itrations, after an initial, discarded, 'warmup' period during the sampler step size and diagonal mass matrix was tuned, and the regios of highest density located. Convergence was assessed by visual assessment of chains, and ensuring that the potential scale reduction factor for all parameters had values less than 1.1, and that there were at least 1000 effective samples for each parameter.
